Perturbed Gait Data

### 2014-11-24 paper.tex
Changed the histogram to a box plot.
I removed the redundancy of stride freq and stride duration.

Figure~\ref{fig:gait-cycle-stats-comparison} compares the distribution in
several statistics of the unperturbed and perturbed gait cycles.

\begin{figure}
  \includegraphics{figures/unperturbed-perturbed-hist-comparison.pdf}
  \caption{Histograms of the average belt speed, cadence, step duration, and
    stride length which compare 120 gait cycles for the unperturbed (purple)
    and perturbed (blue).}
  \label{fig:gait-cycle-stats-comparison}
\end{figure}

>>>>

Figure~\ref{fig:gait-cycle-stats-comparison} compares the distribution in a few
statistics of the unperturbed and perturbed gait cycles.

\begin{figure}
  \includegraphics{figures/unperturbed-perturbed-boxplot-comparison.pdf}
  \caption{Box plots of the average belt speed, stride frequency, and stride
    length which compare 120 gait cycles for the unperturbed (purple) and
    perturbed (blue).}
  \label{fig:gait-cycle-stats-comparison}
\end{figure}
